### 2016-11-16 paper/intro.tex
pass in intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is not uncommon at
large IT organizations.  The Google TAP
system~\cite{google-tap,google-ci} and the Microsoft CloudBuild
system~\cite{prasad-shulte-ieee-microsoft-ci} show that efficiently
building and testing the software are a critically important process
at Google and Microsoft.  The regression testing problem is, however,
not specific to industrial giants.  For example, a recent paper from
the automotive industry reported that test suites can take days to
run~\cite{artl-etal-icst2015}.

@@

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
a recognized problem both in industry and academia, to the best of our
knowledge no prior work has investigated the regression testing
problem in open-source projects.  The alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} to automate testing or
even building a server farm (for increased security), can be a
legitimate approach to mitigate the regression testing problem at
large organizations.  Note that this alternative can be used
irrespective of complementary approaches to save testing costs (e.g.,
test selection).  For example, as of August 2013, the Groupon PWA
system, which powers the \url{groupon.com} website, included over 19K
tests.  To run all those tests under 10m, Groupon used a cluster of 4
computers with 24 cores each~\cite{kim-etal-fse2013}.  For open-source
projects and lower-budget projects, it is still important to run test
suites efficiently in commodity hardware.

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite, which can lead to late reports
of test failures.  Dealing with high testing costs is particularly
critical at large IT organizations, with massive code and test bases.
The Google TAP system~\cite{google-tap,google-ci} and the Microsoft
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci} provide
evidence on the criticality of the build and testing processes at
these organizations.  Note, however, that the regression testing
problem is not specific to giants from the IT sector.  For example, a
recent paper from the automotive industry reported that test suites
can take days to run~\cite{artl-etal-icst2015}.

@@

Several approaches have been proposed in the literature to optimize
regression testing.  Research has focused mostly on test suite
minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  Although regression testing is
a recognized problem both in industry and academia, to the best of our
knowledge no prior work has investigated the regression testing
problem in open-source projects.  The alternative of renting a cloud
service\footnote{\url{https://clutch.co/cloud}} to automate testing or
even building a server farm (for increased security), can be a
legitimate approach to mitigate the regression testing problem at
large organizations.  Note that this alternative can be used
irrespective of complementary approaches to save testing costs (e.g.,
test selection).  For example, as of August 2013, the Groupon PWA
system, which powers the \url{groupon.com} website, included over 19K
tests.  To run all those tests under 10m, Groupon used a cluster of 4
computers with 24 cores each~\cite{kim-etal-fse2013}.  This paper
assumes that, especially considering open-source projects and
lower-budget projects, running test suites efficiently using commodity
hardware is important.
